NumPy---Array Programming in Python

### 2020-02-07 authors.tex
Update author affiliation
MAINT: Tyler revisions
* adjust name & affiliation

* fix an incorrect reference to the reduction
operation in Figure 1, which should be "f" not
"e"

* fix a singular reference to "scientist" that should
be plural

\author[1]{Charles R Harris}
\author[2,3,*]{K. Jarrod Millman}
\author[2,*]{St\'efan J. van der Walt}
\author[4,*]{Ralf Gommers}
\author[5]{Pauli Virtanen}
\author[6]{David Cournapeau}
\author[7]{Eric Wieser}
\author[80]{Julian Taylor}
\author[2]{Sebastian Berg}
\author[9]{Nathaniel J. Smith}
\author[10]{Robert Kern}
\author[2]{Matti Picus}
\author[11]{Stephan Hoyer}
\author[12]{Marten H. van Kerkwijk}
\author[13]{Matthew Brett}
\author[14]{Allan Haldane}
\author[15]{Jaime Fernandez del Rio}
\author[16]{Mark Wiebe}
\author[4,17,18]{Pearu Peterson}
\author[80]{David M. Cooke}
\author[20]{Pierre Gerard-Marchant}
\author[21]{Kevin Sheppard}
\author[22]{Tyler J. Reddy}
\author[2]{Warren Weckesser}
\author[4]{Hameer Abbasi}
\author[23]{Christoph Gohlke}
\author[4]{Travis E. Oliphant}
\affil[1]{Independent Researcher, Logan, Utah, USA}
\affil[2]{Berkeley Institute for Data Science, University of California, Berkeley, Berkeley, CA, USA}
\affil[3]{Division of Biostatistics, University of California, Berkeley, Berkeley, CA, USA}
\affil[4]{Quansight LLC, Austin, TX, USA}
\affil[5]{Department of Physics and Nanoscience Center, University of Jyv\"askyl\"a, Jyv\"askyl\"a, Finland}
\affil[6]{Mercai JP, Tokyo, Japan}
\affil[7]{Department of Engineering, University of Cambridge, Cambridge, UK}
\affil[9]{Independent Researcher, Berkeley, Berkeley, CA, USA}
\affil[10]{Enthought, Inc., Austin, TX, USA}
\affil[11]{Google Research, Mountain View, CA, USA}
\affil[12]{Department of Astronomy \& Astrophysics, University of Toronto, Toronto, ON, Canada}
\affil[13]{School of Psychology, University of Birmingham, Edgbaston, Birmigham, UK}
\affil[14]{Department of Chemistry, Temple University, Philadelphia, PA, USA}
\affil[15]{Google, Zurich, Switzerland}
\affil[16]{AWS Thinkbox, Seattle, Washington, USA}
\affil[17]{Independent Researcher, Saue, Estonia}
\affil[18]{Department of Mechanics and Applied Mathematics, Institute of Cybernetics at Tallinn Technical University, Tallinn, Estonia}
\affil[20]{France-IX, France}
\affil[21]{Department of Economics, University of Oxford, Oxford, UK}
\affil[22]{Los Alamos National Laboratory, Los Alamos, NM, USA}
\affil[24]{Biomedical Engineering Department, University of California, Irvine, Irvine, CA, USA}
\affil[80]{Not sure}
\affil[*]{numpy.articles@gmail.com}

>>>>

\author[1]{Charles R Harris}
\author[2,3,*]{K. Jarrod Millman}
\author[2,*]{St\'efan J. van der Walt}
\author[4,*]{Ralf Gommers}
\author[5]{Pauli Virtanen}
\author[6]{David Cournapeau}
\author[7]{Eric Wieser}
\author[80]{Julian Taylor}
\author[2]{Sebastian Berg}
\author[9]{Nathaniel J. Smith}
\author[10]{Robert Kern}
\author[2]{Matti Picus}
\author[11]{Stephan Hoyer}
\author[12]{Marten H. van Kerkwijk}
\author[13]{Matthew Brett}
\author[14]{Allan Haldane}
\author[15]{Jaime Fernandez del Rio}
\author[16]{Mark Wiebe}
\author[4,17,18]{Pearu Peterson}
\author[80]{David M. Cooke}
\author[20]{Pierre Gerard-Marchant}
\author[21]{Kevin Sheppard}
\author[22]{Tyler Reddy}
\author[2]{Warren Weckesser}
\author[4]{Hameer Abbasi}
\author[23]{Christoph Gohlke}
\author[4]{Travis E. Oliphant}
\affil[1]{Independent Researcher, Logan, Utah, USA}
\affil[2]{Berkeley Institute for Data Science, University of California, Berkeley, Berkeley, CA, USA}
\affil[3]{Division of Biostatistics, University of California, Berkeley, Berkeley, CA, USA}
\affil[4]{Quansight LLC, Austin, TX, USA}
\affil[5]{Department of Physics and Nanoscience Center, University of Jyv\"askyl\"a, Jyv\"askyl\"a, Finland}
\affil[6]{Mercai JP, Tokyo, Japan}
\affil[7]{Department of Engineering, University of Cambridge, Cambridge, UK}
\affil[9]{Independent Researcher, Berkeley, Berkeley, CA, USA}
\affil[10]{Enthought, Inc., Austin, TX, USA}
\affil[11]{Google Research, Mountain View, CA, USA}
\affil[12]{Department of Astronomy \& Astrophysics, University of Toronto, Toronto, ON, Canada}
\affil[13]{School of Psychology, University of Birmingham, Edgbaston, Birmigham, UK}
\affil[14]{Department of Chemistry, Temple University, Philadelphia, PA, USA}
\affil[15]{Google, Zurich, Switzerland}
\affil[16]{AWS Thinkbox, Seattle, Washington, USA}
\affil[17]{Independent Researcher, Saue, Estonia}
\affil[18]{Department of Mechanics and Applied Mathematics, Institute of Cybernetics at Tallinn Technical University, Tallinn, Estonia}
\affil[20]{France-IX, France}
\affil[21]{Department of Economics, University of Oxford, Oxford, UK}
\affil[22]{CCS-7, Los Alamos National Laboratory, Los Alamos, NM, USA}
\affil[23]{Laboratory for Fluorescence Dynamics, Biomedical Engineering Department, University of California, Irvine, Irvine, CA, USA}
\affil[80]{Not sure}
\affil[*]{numpy.articles@gmail.com}

### 2020-02-07 body.tex
Fix spelling of PyData/Sparse.
MAINT: Tyler revisions
* adjust name & affiliation

* fix an incorrect reference to the reduction
operation in Figure 1, which should be "f" not
"e"

* fix a singular reference to "scientist" that should
be plural

Other array-aware functions, such as \code{sum}, \code{mean}, and \code{maximum}, perform
element-by-element \emph{reductions}, aggregating results across one,
multiple, or all axes of a single array.
For example, summing an $n$-dimensional array over $d$ axes results in a
$(n-d)$-dimensional array (Fig.~\ref{fig:array-concepts}e).

@@

%CuPy, Sparse, and JAX the most prominent examples---while others have
%NumPy-inspired semantics but, often due to their development history, deviate in places.
%Wherever there are such deviations, we often observe users gently requesting,
%and developers evolving the software step by step toward the NumPy API.

@@

\emph{Python} is an open-source, general-purpose, interpreted programming language
well-suited to standard programming tasks such as cleaning data,
interacting with web resources, and parsing text.
Adding fast array operations and linear algebra allows scientist to do all
their work within a single language---and one that has the advantage of
being famously easy to learn and teach.
In fact, Python's adoption as a primary learning language in universities
has further popularized NumPy as a tool of choice for modern data science.

>>>>

Other array-aware functions, such as \code{sum}, \code{mean}, and \code{maximum}, perform
element-by-element \emph{reductions}, aggregating results across one,
multiple, or all axes of a single array.
For example, summing an $n$-dimensional array over $d$ axes results in a
$(n-d)$-dimensional array (Fig.~\ref{fig:array-concepts}f).

@@

%CuPy, PyData/Sparse, and JAX the most prominent examples---while others have
%NumPy-inspired semantics but, often due to their development history, deviate in places.
%Wherever there are such deviations, we often observe users gently requesting,
%and developers evolving the software step by step toward the NumPy API.

@@

\emph{Python} is an open-source, general-purpose, interpreted programming language
well-suited to standard programming tasks such as cleaning data,
interacting with web resources, and parsing text.
Adding fast array operations and linear algebra allows scientists to do all
their work within a single language---and one that has the advantage of
being famously easy to learn and teach.
In fact, Python's adoption as a primary learning language in universities
has further popularized NumPy as a tool of choice for modern data science.
